Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-10-16 analysis/paper/paper.qmd
add doi

All data treatment, analyses and visualization were performed in the R environment [@core2021team]. Our R code and data including the raw images are openly available online: https://github.com/parkgayoung/CTtps as well as https://osf.io/eb8mx/ to enable full reproducibility [@marwick2017computational].

>>>>

All data treatment, analyses and visualization were performed in the R environment [@core2021team]. Our R code and data including the raw images are openly available online: https://github.com/parkgayoung/CTtps as well as DOI: 10.17605/OSF.IO/EB8MX to enable full reproducibility [@marwick2017computational].
